```{r}
df <- read.csv("D:/Jurnal/Data Science/Data Cleaning in R/train.csv")
```

```{r}
#import Library
library(tidyverse)
library(ggplot2)
library(dplyr)
View(df)
```

1. Number of House Style Sold
```{r}
df %>%
  count(HouseStyle) %>%
  ggplot(aes( reorder(x = HouseStyle, n), y = n)) +
  geom_bar(stat ="identity", fill ="orange") +
  geom_label(aes(label=n)) +
  ggtitle("Number of House Style Sold")+
  xlab("House Style")+
  ylab("Unit Sold")+
  theme(axis.title.x = element_text(family = "arial", size = 12))+
  theme(axis.title.y = element_text(family = "arial", size = 12))

```
Insight 1: 1 Story house is the most sold house in Ames
Insight 2: 2.5 fin house is the least sold house in Ames
Insight 3: 2 Story house is the second most sold house in Ames
Insight 4: 1 story and 2 story house is the most sold house in Ames


2. Difference of Fondation across Year Build
```{r}
df %>%
  ggplot(aes(x = YearBuilt))+
  geom_density(aes(fill = factor(Foundation)), alpha = 0.5)+
  ggtitle("Difference of fondation across Year Build")+
  xlab("Year Built")+
  theme(axis.title.x = element_text(family = "arial", size = 12))+
  theme(axis.title.y = element_text(family = "arial", size = 12))
```
Insight 1: Most of the house built around 1900 used stone as fondation
Insight 2: Number of house built with stone fondation started to dissappear in 1980
Insight 3: Currently most used fondation is concrete
Insight 4: Brick tile fondation started to replace stone fondation around 1930


3. House Price Based on Rating
```{r}
df%>%
  #3.Membuat rating rumah berdasarkan overall quality
  mutate( Rating = case_when(
    OverallQual <= 2 ~ "Poor",
    OverallQual >2 & OverallQual <= 4 ~ "Fair",
    OverallQual >4 & OverallQual <= 6 ~ "Good",
    OverallQual >6 & OverallQual <= 8 ~ "Satisfactory",
    OverallQual >8 & OverallQual <= 10 ~ "Exellent", ))%>%
  ggplot(aes(x = reorder(Rating, SalePrice), y = SalePrice)) +
  geom_boxplot(fill = "orange")+
  ggtitle("House Sale Price Based on Rating")+
  xlab("Rating")+
  ylab("Sale Price")+
  theme(axis.title.x = element_text(family = "arial", size = 12))+
  theme(axis.title.y = element_text(family = "arial", size = 12))

```
Insight 1: House with rank exellent is the most expensive house
Insight 2: House with rank poor is the least expensive house
Insight 3: House with rank exellent is the most bought house
Insight 4: house with rank exellent tend to have more variative price

4. House Price Based on Garage Area Size across Different Sale Condition
```{r}
df %>%
  ggplot(aes(x = GarageArea, y = SalePrice, alpha = 0.7))+
  geom_point()+
  geom_smooth(method = 'lm', se = FALSE)+
  facet_wrap("SaleCondition")+
  ggtitle("House Price based on Garage Area Size across different Sale Condition")+
  xlab("Garage Area Size")+
  ylab("Sale Price")+
  theme(axis.title.x = element_text(family = "arial", size = 12))+
  theme(axis.title.y = element_text(family = "arial", size = 12))

```
Insight 1: The larger the garage area, the more expensive a house would be
Insight 2: if the house sale is held among family members, the price tend to be cheaper
